---
title: "Scottish Government RAP Self Assessment"
format:
  html:
    page-layout: custom
    css: styles.css
    embed-resources: true
server: shiny
---

This tool provides a way for statisticians in the Scottish Government to self-assess their progress in developing [Reproducible Analytical Pipelines](https://analysisfunction.civilservice.gov.uk/support/reproducible-analytical-pipelines/).
    
```{r, include = FALSE}
#| context: setup

library(shiny)
library(dplyr)
library(here)
library(readr)
library(purrr)
library(tibble)

walk(list.files("modules", ".R$", full.names = TRUE), source)

criteria <- read_csv(here("criteria.csv"), show_col_types = FALSE) %>%
    mutate(id = paste0("Q", id))

options <- c(`Complete` = "yes", 
             `In progress` = "progress", 
             `Not started` = "no",
             `Not assessed` = "not_assessed")

levels <- c(`Aspiring` = 0,
            `Fundamental` = 1,
            `Intermediate` = 2,
            `Advanced` = 3)
```



::: {.panel-sidebar}

```{r}
sidebarPanel(
   metadata_ui("metadata"),
   br(),
   download_report_ui("report"),
   br(),
   br(),
   download_csv_ui("csv")
)
```

:::

::: {.panel-center}

## Level 0 - Aspiring RAP

```{r}
form_ui("form", criteria[1,], levels, options)
```

::: {.callout-tip collapse="true"}
## What does this mean?

R is the most commonly used software in the Scottish Government.
:::

```{r}
form_ui("form", criteria[2,], levels, options)
```

## Level 1 - Fundamental RAP

```{r}
form_ui("form", criteria[1,], levels, options)
```

```{r}
form_ui("form", criteria[1,], levels, options)
```

::: {.callout-tip collapse="true"}
## What does this mean?

R is the most commonly used software in the Scottish Government.
:::
```{r}
form_ui("form", criteria[1,], levels, options)
```

::: {.callout-tip collapse="true"}
## What does this mean?

R is the most commonly used software in the Scottish Government.
:::
```{r}
form_ui("form", criteria[1,], levels, options)
```

::: {.callout-tip collapse="true"}
## What does this mean?

R is the most commonly used software in the Scottish Government.
:::
```{r}
form_ui("form", criteria[1,], levels, options)
```

::: {.callout-tip collapse="true"}
## What does this mean?

R is the most commonly used software in the Scottish Government.
:::
```{r}
form_ui("form", criteria[1,], levels, options)
```

::: {.callout-tip collapse="true"}
## What does this mean?

R is the most commonly used software in the Scottish Government.
:::
:::

```{r}
#| context: server

assessment <- callModule(form_server, "form", criteria$id)

data_output <- reactive({
   criteria |>
      rowwise() |> 
      mutate(
         status = assessment()[[id]],
         status_label = case_when(
            status == "not_assessed" ~ "Not assessed",
            TRUE ~ names(options)[match(status, options)]
         )
      )
})

metadata <- callModule(metadata_server, "metadata")

callModule(download_csv_server, "csv", data_output)

callModule(download_report_server, "report", data_output, levels, options, metadata)
```
